\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{Network Engineer L6 \hfill \textrm{\textmd{Sep. 2024 --- Present}}\\
	Network Engineer L5 (Previously Senior Network Engineer) \hfill \textrm{\textmd{Feb. 2019 --- Sep. 2024}}}
\subtext{Netflix \hfill Remote}
\begin{zitemize}
	\item Automate router and switch configuration using Go, Python, and
	internal management framework tools
	\item Manage day-to-day operations of Netflix backbone, peering
	connectivity, and internal corporate hand-offs
	\item Optimize network monitoring system to provide visibility
	into network reliability, incidents, and performance
	\item Implement router and switch configurations for Arista and
	Juniper devices
	\item Respond to streaming incidents and perform deep-dive
	analysis of quality of experience impacts
	\item Actively support diversity and inclusion initiatives,
	through cross-functional work with executive management,
	human resources, and content/creative teams
	\item Mentor other employees to ensure their success at Netflix.
\end{zitemize}

%====================
% EXPERIENCE B
%====================

\subsection{Lead Network Engineer (Previously Senior Network Engineer) \hfill \textrm{\textmd{July 2011 --- Feb. 2019}}}
\subtext{CenturyLink / Former Level 3 Communications \hfill Broomfield, CO}
\begin{zitemize}
	\item Collaborated with operations, development, sales, customer support,
	and other teams to transfer knowledge and support content
	distribution network (CDN)
	\item Improved efficiency throughout 150+ site, 15,000+ server,
	world-wide, top-tier CDN
	\item Provided expert advice to other business units about internet
	structure and interconnection, with focus on optimization of content delivery across
	multiple peer, customer, and transit networks
	\item Develop custom custom BGP route collector (including
	implementation of BGP protocol at the byte level) and processing infrastructure
	to allow third party ISPs to signal content delivery preferences
	\item Lead system engineer for CDN DNS global load balancing and
	rendezvous system
\end{zitemize}


%====================
% EXPERIENCE C
%====================
\subsection{Consultant (Part-Time) \hfill \textrm{\textmd{Apr. 2012 --- Feb. 2013}}\\
	Director of Information Technology \hfill \textrm{\textmd{Oct. 2009 --- June 2011}}\\
	Senior System Administrator \hfill \textrm{\textmd{Dec. 2008 --- Oct. 2009}}}
\subtext{Local Matters, Inc. \hfill Denver, CO}
\begin{zitemize}
	\item Promoted from Senior System Administrator to director of
	information technology team
	\item Managed Information Technology department, including
	oversight of IT staff, planning, and direction
	\item Mentored team members in technical skills, such as
	Unix/Linux, Apache, Perl, and networking
	\item Managed vendor relationships for IT equipment and
	services, optimizing for cost-savings
	\item Extended configuration management environment to create
	full audit capability for system administration work,
	utilizing Puppet
	\item Developed custom on-demand portal to allow development and
	QA organizations to start and stop new AWS instances as
	necessary
	\item Installed and configured multi-site storage area network
	based on NetApp appliances
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{Network Engineering and Operations Supervisor \hfill \textrm{\textmd{May 2008 --- Dec. 2008}}\\
	Database Administrator \hfill \textrm{\textmd{May 2004 --- May 2008}}\\
	Information Security Engineer (PKI) \hfill \textrm{\textmd{Oct.  2001 --- Apr. 2004}}}
\subtext{State of Wyoming Dept. of Administration \& Information \hfill Cheyenne, WY}
\begin{zitemize}
	\item Promoted to network management from senior technologist
	position based on technical skill
	\item Managed staff responsible for architecture, engineering,
	and operations of the State of Wyoming executive branch
	network, including network engineers, low voltage
	electricians, and network operators
	\item Oversaw 24x7 support of State network functions
	\item Responsible for annual budget including salary, hardware,
	support, and circuit expenses
	\item Participated in state-wide technology leadership committees
	\item Partnered with judicial, legislative, and educational
	counterparts, to provide cost-savings to the State's
	four independent government branches
	\item Wrote policies and procedures for Public Key
	Infrastructure (PKI), including initial development of
	Certificate Policy, practices documentation, and
	technical documentation with goal of Federal PKI (FPKI)
	integration
	\item Created State of Wyoming border security architecture,
	utilizing Checkpoint firewalls and VPN edge devices
	\item Implemented distributed intrusion detection system (IDS)
	\item Developed initial architecture for Wyoming E-Government
	initiative's single sign-on (SSO) system for citizens and
	employees
	\item Participated in budget and rate-setting processes
	\item Managed and optimized Microsoft SQL (MSSQL) system
	\item Developed custom SQL queries, reports, and Transact-SQL
	(T/SQL) packages to support internal systems and
	developers
	\item Provided internal support as subject matter expert in
	network design, security, Windows/Microsoft application
	architecture, database management, intrusion
	detection/prevention, forensic analysis, data center
	operations, and internet protocols
\end{zitemize}
%====================
% EXPERIENCE E
%====================
\subsection{Senior Software Engineer \hfill \textrm{\textmd{Sep. 2000 --- Oct. 2001}}}
\subtext{MotionGrid \hfill Laramie, WY}
\begin{zitemize}
	\item Mentored junior development staff
	\item Developed J2EE compliant web applications, utilizing
	WebLogic, Enterprise Java Beans (EJB), and Java Servlet
	Pages (JSP)
	\item Administered Unix and Windows systems to support
	development staff
	\item Implemented Microsoft Internet Information Services (IIS)
	web applications using ASP with COM components
	\item Initiated sound software engineering practices throughout
	organization, such as version control of code and
	database objects, separate build and production
	environments, and defect tracking
\end{zitemize}

%====================
% EXPERIENCE F
%====================
\subsection{Fraud Detection and Billing Engineer \hfill \textrm{\textmd{Oct. 1999 --- Sep. 2000}}}
\subtext{Affinia, Inc. \hfill Denver, CO}
\begin{zitemize}
	\item Designed and developed e-commerce advertising fraud
	detection system
	\item Implemented custom billing and payment system, integrating
	with Solomon accounting system
	\item Developed Perl-based statistical anomaly detection
	software
	\item Performed data warehousing tasks using Oracle RDBMS,
	through PL/SQL procedure and report creation
	\item Served as peer lead for cross-functional teams during
	fraud detection, billing, and payment processes
\end{zitemize}

%====================
% EXPERIENCE G
%====================
\subsection{Technical Lead \hfill \textrm{\textmd{May 1998 --- Oct. 1999}}}
\subtext{UPDATE Systems, Inc. \hfill Boulder, CO}
\begin{zitemize}
	\item Established network and communication systems in initial
	business location
	\item Oversaw development and functional requirement gathering
	during first two versions of flagship software product
	\item Implemented web software and Unix daemons in Perl on
	Linux, FreeBSD, and BSDi
	\item Managed day-to-day IT needs, including email, corporate
	web presence, security, and Windows client functionality
\end{zitemize}

%====================
% EXPERIENCE H
%====================
\subsection{Software Engineer and Network Administrator \hfill \textrm{\textmd{Jan. 1996 --- May 1998}}}
\subtext{Wind River Visual Communication \hfill Laramie, WY}
\begin{zitemize}
	\item Created and managed web hosting environment, including
	management of web servers, routers, switches, and firewalls
	\item Managed Mac, Windows, Linux, and FreeBSD servers and
	workstations
\end{zitemize}

\end{document}
